Using R to help plan the <br> future of transport

### 2019-01-14 ms-meetup-nov18.Rmd
new deploy
final deploy
fix example code to visualize the *P*romenade

```{r osmdata-pbf, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sf (file = "ms48155.pbf")
```

@@

```{r promenade-data2, eval = FALSE}
library (osmdata)
promenade <- opq ("münster de") %>%
    add_osm_feature (key = "highway") %>%
    add_osm_feature (key = "name", value = "promenade", #<<
                     value_exact = FALSE) %>%           #<<
    osmdata_sf ()
```

@@

```{r promenade-data3, eval = FALSE}
library (osmdata)
promenade <- opq ("münster de") %>%
    add_osm_feature (key = "highway") %>%
    add_osm_feature (key = "name", value = "promenade",
                     value_exact = FALSE) %>%
    osmdata_sf ()
library (mapview)
mapview (promenade$osm_lines) #<<
```

>>>>

```{r osmdata-all, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sf ()
```

@@

```{r promenade-data2, eval = FALSE}
library (osmdata)
promenade <- opq ("münster de") %>%
    add_osm_feature (key = "highway") %>%
    add_osm_feature (key = "name", value = "Promenade", #<<
                     value_exact = FALSE) %>%           #<<
    osmdata_sf ()
```

@@

```{r promenade-data3, eval = FALSE}
library (osmdata)
promenade <- opq ("münster de") %>%
    add_osm_feature (key = "highway") %>%
    add_osm_feature (key = "name", value = "Promenade",
                     value_exact = FALSE) %>%
    osmdata_sf ()
library (mapview)
mapview (promenade$osm_lines) #<<
```
